FoRTE baseline

### 2019-04-29 analysis/paper/paper.Rmd
Add parameter vs. structural uncertainty figure

@@

**TODO**: Structural vs. parameteric uncertainty

>>>>

```{r within-vs-across, fig.cap = within_vs_across_cap, fig.dim = c(6, 6)}
within_vs_across_cap <- paste(
  "Comparison of parameteric uncertainty within ensembles (colored bars, colored by model type)",
  "and \"structural\" uncertainty (variance in ensemble means; black bar) by output variable.",
  "Output variables are expressed as growing season averages for all years after 1910."
)
readd(within_across_plot)
```

Take-away: Overall, structural uncertainty (variance in ensemble means across structures) is comparable or lower than parameter uncertainty (uncertainty within ensembles for a given structure).

`r mdcap within_vs_across_cap`

@@
